Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/appendix.tex
update concretization proof with new definitions

@@

\vspace{2em}
\begin{thm}
  For any $\Gamma$, $f$, $G$ such that $\Gamma$ is well-formed with respect to $G$,
  $$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$

  \begin{proof} \text{ }

@@

    Next we compute $compile(con(pol,\Gamma,f))$:

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f))  \\
                          & \\
                         =& compile_{ABGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
                          &  ) \\
    \end{array} \]

@@

    \vspace{1em}
    Similarly, we can compute $compile(pol)$:

    \[ \begin{array}{ll}
        & compile(pol)  \\
                      & \\
                     =& compile_{ABGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
                      & ) \\
    \end{array} \]

@@

    \begin{itemize}
      \item each $PG^A_i$ and $PG_ij$ are related by $f_{pg}$
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
    \end{itemize}

  \[ \begin{array}{l}
     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%

Unfold definition of compile

  \[ \begin{array}{l}
     ~~~~~ con(\{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}, \Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow con(rc,\ell,\Gamma,f,G)) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_n) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = con(\bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}, \ell,\Gamma,f,G) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(V^A), \\
     ~~~~~~~~~ rc = \bigcup_i~ con(\{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}, \ell,\Gamma,f,G) \} \\
  \end{array} \]%

  \vspace{1em}
  \textbf{Case 1}: Assume $t_i = pfx$. Look at:

  \[ \begin{array}{l}
     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true},\ell,\Gamma,f,G) \}) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ con(\{ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     = \textbf{compile}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
  \end{array} \]%

>>>>

\ryan{Update me}

@@

\vspace{2em}
\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:

  $$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f),G)$$

  \vspace{1em}
  \begin{proof} \text{ }

@@

    Next we compute $compile(con(pol,\Gamma,f), G)$:

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f), G)  \\
                          & \\
                         =& compile_{ABGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
                          &  ) \\
    \end{array} \]

@@

    \vspace{1em}
    Similarly, we can compute $compile(pol, G^A)$:

    \[ \begin{array}{ll}
        & compile(pol,G^A)  \\
                      & \\
                     =& compile_{ABGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
                      & ) \\
    \end{array} \]

@@

    \begin{itemize}
      \item each $PG^A_i$ and $PG_{ij}$ are related by $f_{pg}$
      \vspace{-.2em}
      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
    \end{itemize}

  \[ \begin{array}{l}
     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%

Unfold definition of $\text{compile}_\text{ABGP}$

  \[ \begin{array}{l}
     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  \vspace{1em}
  \textbf{Case 1}: Assume $t_i = pfx_{i1}$. Look at:

  \[ \begin{array}{l}
     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

  Rewrite $con$ on $in$

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \} \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ con([~ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     = \textbf{compile}_\textbf{ABGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
  \end{array} \]%
